OptiFit: a fast method for fitting amplicon sequences to existing OTUs

### 2021-06-23 paper/paper.Rmd
Spell out 'snakemake' for Rmd param

---
title: "OptiFit: a fast method for fitting amplicon sequences to existing OTUs"
date: '`r Sys.Date()`'
bibliography: references.bib
output:
  pdf_document:
    keep_tex: false
    includes:
      in_header: preamble.tex
      before_body: head.tex
    number_sections: false
    toc: false
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs", output_format = "all") })
csl: msystems.csl
fontsize: 12pt
geometry: margin=1.0in
repository_url: https://github.com/SchlossLab/OptiFitAnalysis
params:
    smk: "none"
---

@@

```{r deps, message = FALSE}
library(cowplot)
library(here)
library(knitr)
library(schtools)
library(tidyverse)
snakemake <- params$smk
load(here(snakemake@input[['rda']]))
```
```{r figs-meta}
figures_meta <- yaml::read_yaml(here('config', 'figures.yaml'))
figs <- function(fig_name, attribute) {
  value <- figures_meta[[fig_name]][[attribute]]
  if (attribute != 'cap') {
    value <- eval(parse(text = value))
  }
  return(value)
}
```

>>>>

---
title: "OptiFit: a fast method for fitting amplicon sequences to existing OTUs"
date: '`r Sys.Date()`'
bibliography: references.bib
output:
  pdf_document:
    keep_tex: false
    includes:
      in_header: preamble.tex
      before_body: head.tex
    number_sections: false
    toc: false
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs", output_format = "all") })
csl: msystems.csl
fontsize: 12pt
geometry: margin=1.0in
repository_url: https://github.com/SchlossLab/OptiFitAnalysis
params:
    snakemake: "none"
---

@@

```{r deps, message = FALSE}
library(cowplot)
library(here)
library(knitr)
library(schtools)
library(tidyverse)
snakemake <- params$snakemake
load(here(snakemake@input[['rda']]))
figures_meta <- yaml::read_yaml(here('config', 'figures.yaml'))
figs <- function(fig_name, attribute) {
  value <- figures_meta[[fig_name]][[attribute]]
  if (attribute != 'cap') {
    value <- eval(parse(text = value))
  }
  return(value)
}
```
